---
number_sections: true
fig_caption: yes
output:
  bookdown::pdf_document2:
    toc: false
  citation_package: natbib
fontsize: 12pt 
indent: true
header-includes:
- \usepackage{amsmath}
- \numberwithin{equation}{section}
- \usepackage{setspace}\doublespacing
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{indentfirst}
papersize: a4
bibliography: C:/Users/shain/Desktop/multipleStrategies/proposal/ref.bib
biblio-style: apalike
csl: C:/Users/shain/Desktop/multipleStrategies/proposal/harvard-educational-review.csl
---

\title{\vspace{20mm}TITLE HERE}
\maketitle
\thispagestyle{empty} 
\vspace*{90px}
\begin{center}
A Thesis Proposal Presented to\\
The Faculty of the School of Statistics\\
University of the Philippines, Diliman\\
\vspace*{100px}
In Partial Fulfillment\\
of the Requirements for the Degree of\\
Master of Science in Statistics\\
2nd Semester A.Y. 20**-20**

\vspace*{90px}
by\\
Shaine Rosewel P. Matala
\end{center}


\newpage



# Abstract {-}

```{r, child = "child/00_abstract.Rmd"}

```

\newpage

\tableofcontents

\newpage

# Introduction

```{r, child = "child/01_introduction.Rmd"}

```

# Literature Review

```{r, child = "child/02_rrl.Rmd"}

```

# Methodology

```{r, child = "child/03_methodology.Rmd"}

```

# Results

```{r, child = "child/04_results.Rmd"}
hist(rnorm(10000))
```

# Discussion

```{r, child = "child/05_discussion.Rmd"}

```

# References

<div id="refs"></div>

# Appendices {-}

```{r, child = "child/06_appendix.Rmd"}

```
